---
title: "Citations"
output:
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: true
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

## Google Scholar Mentions

This tracks the cumulative number of mentions of the keywords `anvil nhgri` on Google Scholar. For example, for 2026 only, we'd see the number of hits with the following url: https://scholar.google.com/scholar?hl=en&as_sdt=0%2C21&as_ylo=2026&q=anvil+nhgri&btnG=

This data is fairly small and static, and is thus stored in the `data/` directory.

```{r echo = FALSE, hide = TRUE, message = FALSE}
source(file.path("R","scholar_plot_functions.R"))
make_scholar_hits_plot()
```

## Preview

Currently this is capped at reporting 10 citations per paper. But this will be fixed soon.

```{r, echo = FALSE, hide = TRUE, message = FALSE}
root_dir <- rprojroot::find_root(rprojroot::has_dir(".git"))
yaml <- yaml::read_yaml(file.path(root_dir, "_config_automation.yml"))

citations <- readr::read_tsv(file.path("metricminer_data", "citations", "citations.tsv"))

```

```{r, include = FALSE}
## For google
# citations <- googlesheets4::read_sheet(yaml$citations_googlesheet)
```

Here we show how to get the total counts per original paper:

```{r,message=FALSE}
library(dplyr)
# here we remove duplicates if there are any of the same titles of citing papers for each original paper and then get a count of the number of rows for each original paper (aka how many times it is cited)
citations %>%
  distinct(original_paper, cite_titles, .keep_all = TRUE) %>%
  count(original_paper)
```

## Data information

Column information:

- `original_paper` shows papers that we have captured citation information about
- `cite_titles` shows papers that cite the original paper
- `links`column shows the link for the paper that cites the original paper (the `cite_titles` papers).

```{r, message = FALSE}
knitr::kable(citations)
```
