---
title: "GitHub"
output:
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: true
date: "`r format(Sys.time(), '%d %B, %Y')`"

---

## Preview

```{r, echo = FALSE, hide = TRUE, message=FALSE, warning = FALSE}
library(ggplot2)
library(magrittr)

root_dir <- rprojroot::find_root(rprojroot::has_dir(".git"))
yaml <- yaml::read_yaml(file.path(root_dir, "_config_automation.yml"))

## For github
github_overall <- readr::read_tsv(file.path("metricminer_data", "github", "github.tsv"))
github_timecourse <- readr::read_tsv(file.path("metricminer_data", "github", "github_timecourse.tsv"))
```

Contributions to a repository example:

```{r echo = FALSE, hide = TRUE, message=FALSE, warning = FALSE}
github_overall %>%
  ggplot(aes(x = repo_name, y = total_contributions)) +
  geom_bar(stat = "identity", fill = "lavender") +
  theme_classic()
```

Views of a GitHub Repository over time

```{r echo = FALSE, hide = TRUE, message=FALSE}
github_timecourse %>%
  ggplot(aes(x = timestamp, y = count_views, fill = repo, color = repo)) +
  geom_line(stat = "identity") +
  theme_classic() +
  ylab("date")
```

## Data information

Data information for `github overall data`:

- `num_forks` shows the number of times this repo has been forked. NA means it has never been forked.
- `num_contributors` how many people have contributed to this repo
- `num_stars` how many people have starred this repo?
- `health_percentage` what percentage of ["good software health" items as described by GitHub](https://docs.github.com/en/communities/setting-up-your-project-for-healthy-contributions/about-community-profiles-for-public-repositories) does this repo have?

```{r, message=FALSE}
knitr::kable(github_overall)
```

Data information for `github timecourse`:

- `timestamp` shows the date the counts correspond to
- `count_clones` tells the number of clones made on this day. NAs generally indicate no one cloned the repository that day.
- `unique_clones` tells how many people did these clones come from? NAs generally indicate no one cloned the repository that day.
- `count_views` how many views did the repo get on this day? NAs generally indicate no one viewed the repository that date
- `unique_views` how many people were those views from? NAs generally indicate no one viewed the repository that date

```{r, message=FALSE}
knitr::kable(github_timecourse)
```
